\subsection{Demand Driven Cycamore Archetype: Goals}
\begin{frame}
  \frametitle{Demand Driven Cycamore Archetype: Goals}
  % a comment

\begin{block}{Goals for the Demand Driven Cycamore Archetype (d3ploy)}
\begin{enumerate}
	\item Create an archetype that gives \Cyclus the capability to deploy supporting fuel cycle facilities to meet front-end and back-end demands of the fuel cycle. 
	\item Develop three types of prediction algorithms to achieve this capability: Non-optimizing, Deterministic Optimizing, Stochastic Optimizing. Each will improve on the previous algorithm to make the predictions more accurate. 
\end{enumerate}
\end{block}

\begin{block}{How it works}
User-specified inputs: 
\begin{enumerate}
	\item A commodity whose demand drives deployment
	\item Growth rate of that demand
	\item The facilities in the simulation able to meet that demand
\end{enumerate}
Using the user-specified inputs, the archetype will deploy facilities and supporting facilities to meet the demand for the specified commodity and the supporting commodities required to produce it. 
\end{block}

\end{frame}

\subsection{Demand Driven Cycamore Archetype:  Current work}
\begin{frame}
  \frametitle{Demand Driven Cycamore Archetype: Current Work}
% a comment

\begin{block}{People involved in this project}
	\textbf{University of South Carolina}\\
	PI: Dr. Anthony Scopatz \\
	 Postdoc Researcher: Dr. Robert Flanagan \\
	\textbf{University of Illinois at Urbana Champaign} \\
	Co-PI: Dr. Kathryn Huff \\
	Graduate Student Researchers: Gwendolyn Chee and Jin Whan Bae (Teddy)
\end{block}

\begin{block}{Current work being done by UIUC}
	\begin{enumerate}
		\item Numerical experiments to test d3ploy
		\item The tests are described in reports written for each type of prediction algorithm. 
                \item The report for the non-optimizing case can be found at \cite{bae_numerical_2018}. 
	\end{enumerate}
\end{block}

\begin{block}{Where is d3ploy?}
	d3ploy can be found in this github repository: \url{https://github.com/ergs/d3ploy}
	The tests are being developed there as well, though the reports are in  
        \url{https://github.com/arfc/ddca_numerical_exp}
\end{block}

\end{frame}
